\documentclass[12pt,a4paper,twoside,openany]{book}

\input{settings/layout_commands.tex}

\usepackage{subcaption}
\usepackage{graphicx}
\graphicspath{{img/}{../img/}{../../img/}}
\usepackage{caption}
\usepackage{amsmath}

\usepackage{xargs}
\usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
%\usepackage{cite}

% Mode:
%\visualmode{print} % print mode 
\visualmode{screen} % screen mode 


% Language:
%\thesislanguage{czech}
\thesislanguage{english}

\thesisauthor{Artyom Voronin}
\thesissupervisor{Martin Brablc}
\thesistitle{Predictive maintenance of pneumatic pistons }


\input{settings/vut_style.tex} % nastaveni stylu dokumentu

\begin{document}
	
\VUTtitle{pages/titulni_color.pdf}{pages/zadani_color.pdf} 
%\VUTtitle{pages/titulni_color.pdf}{blank} % Use when print


\abstract{ % abstrakt cesky

Tato práce se zabývá vytvořením simulačního modelu dvojčinného
pneumatického pístu s mechanickou sestavou, včetně modelů snímačů, s
následujícím odhadem parametrů a aproximací chování demonstračního
zařízení. Dalším cílem je prezentace různých přístupů prediktivní údržby
na datové sadě měřené na demonstračním zařízení. Na
měřený datový soubor se aplikovaly signal-based techniky bez použití simulačního
modelu a model-based metody, které vyžadují použití simulačního
modelu.

Výsledkem této práce je ověření možnosti monitorování stavu zařízení pomocí
nainstalovaných senzorů a vyhodnocení efektivity senzorů z hlediska
přesnosti a finančních nákladů.

	}{ % abstrakt anglicky

This thesis deals with creating a simulation model of a double-acting
pneumatic piston with a mechanical assembly, including the sensors models,
with the following parameter estimation and approximation to the behavior
of a demonstration device. Another goal is the demonstration of various
Predictive Maintenance approaches on a dataset measured on a demonstration
device. Applying signal-based techniques to the measured dataset without using
a simulation model and a model-based method that requires the use of a
simulation model. 

The outcome of this work is the verification of the possibility of
monitoring the device's condition state,  using installed sensors, and
evaluating the efficiency of the sensors in terms of accuracy/cost. 
	}{ % klicova slova česky
dvojčinný pneumatický válec, prediktivní údržba, identifikace a detekce
poruch, zbývající doba použitelnosti, PdM, FDI, RUL
	}{ % klicova slova anglicky
    double-acting pneumatic piston, predictive maintenance, fault detection
    and identification, remaining useful life, PdM, FDI, RUL 
    }{ 
    \input{chapters/abstract_extended.tex}
	} % vyrobi i citaci

\acknowledgements{
    I hereby declare that except where specific reference is made to the work of others,
    the contents of this dissertation are original and have not been submitted in whole or in
    part for consideration for any other degree or qualification in this, or any other university.
    This master’s thesis is my own work and contains nothing which is the outcome of work
    done in collaboration with others.
	}{
	Poděkování..
	} % vlozi prohlaseni a podekovani


\vutpagestyle % prepise styl stranky, vlozi obsah


\input{chapters/intro.tex} 
\input{chapters/fdipm.tex}
\input{chapters/overview.tex}
\input{chapters/models.tex}
\input{chapters/alt_models.tex}
\input{chapters/comp_models.tex}
\input{chapters/sb.tex}
\input{chapters/mb.tex}
\input{chapters/conclusion.tex}
\input{chapters/abbreviations.tex}
%\listofffigures
%\listofftables

\bibliography{citations.bib}
\bibliographystyle{plain}


\end{document}
