\begin{thebibliography}{14}


\bibitem{data_ensemble} \textit{Data Ensembles for Condition Monitoring and
Predictive Maintenance} [online]. The MathWorks [cit. 2021-5-21]. Dostupné
z:
https://www.mathworks.com/help/predmaint/ug/data-ensembles-for-condition-monitoring-and-predictive-maintenance.html
    
\bibitem{lit_survey} DUBRAVKO, Miljković. \textit{Fault detection methods:
A literature survey}. 2011.


\bibitem{digit_twin} \textit{Digital Twins for Predictive Maintenance}
[online]. The MathWorks [cit. 2021-5-21]. Dostupné z:
https://explore.mathworks.com/digital-twins-for-predictive-maintenance/landing-36US-760M7.html


\bibitem{dfd_app} \textit{Diagnostic Feature Designer} [online]. [cit.
2021-5-21]. Dostupné z:
https://www.mathworks.com/help/predmaint/ref/diagnosticfeaturedesigner-app.html



\bibitem{fdi_cern2} \textit{Fault detection and isolation an overwiew}
[online]. In: . s.~1-68 [cit. 2020-8-31]. Dostupné z:
https://indico.cern.ch/event/459867/attachments/1187105/1721587/FDI\_CERN.pdf


\bibitem{state_of_art_pdm} HASHEMIAN, H. M. a Wendell C. BEAN.
State-of-the-Art Predictive Maintenance Techniques*. \textit{IEEE
Transactions on Instrumentation and Measurement} [online]. 2011,
\textbf{60}(10), 3480-3492 [cit. 2021-5-21]. ISSN 0018-9456. Dostupné z:
doi:10.1109/TIM.2009.2036347


\bibitem{matlab_intro} \textit{Introduction to Predictive Maintenance with
MATLAB} [online]. [cit. 2021-5-21]. Dostupné z:
https://www.mathworks.com/content/dam/mathworks/ebook/predictive-maintenance-ebook-part1.pdf


\bibitem{isermann_mech} ISERMANN, Rolf. \textit{Mechatronic Systems}
[online]. 2005. London: Springer London, 2003 [cit. 2021-5-21]. ISBN
978-1-85233-930-2. Dostupné z: doi:10.1007/1-84628-259-4


\bibitem{isermann_fdi} ISERMANN, Rolf. \textit{Fault-Diagnosis Systems}
[online]. Berlin, Heidelberg: Springer Berlin Heidelberg, 2006 [cit.
2021-5-21]. ISBN 978-3-540-24112-6. Dostupné z: doi:10.1007/3-540-30368-5


\bibitem{pdm_dyn_systems} LUGHOFER, Edwin a Moamar SAYED-MOUCHAWEH, ed.
\textit{Predictive Maintenance in Dynamic Systems} [online]. Cham: Springer
International Publishing, 2019 [cit. 2021-5-21]. ISBN 978-3-030-05644-5.
Dostupné z: doi:10.1007/978-3-030-05645-2


\bibitem{fdi_site} STANLEY, Greg. \textit{Fault Management - the
Overall Process and Life Cycle of a Fault} [online]. 2020 [cit. 2021-5-21].
Dostupné z:
https://gregstanleyandassociates.com/whitepapers/FaultDiagnosis/Fault-Management/fault-management.htm



\bibitem{matlab_full} \textit{Predictive Maintenance Toolbox User's Guide}
[online]. March 2021. The MathWorks, March 2021 [cit. 2021-5-21]. Dostupné
z: https://www.mathworks.com/help/pdf\_doc/predmaint/predmaint\_ug.pdf


\bibitem{fluid} PHILIP J, Pritchard a Mitchell JOHN W. \textit{Fox and
McDonald's introduction to fluid mechanics}. 9. Nashville, TN: John Wiley,
2015. ISBN ES8-1-118-91265-2.

\bibitem{piston_datasheet} \textit{Round cylinders DSNU/ESNU} [online].
[cit. 2021-5-21]. Dostupné z:
https://www.festo.com/media/pim/156/D15000100122156.PDF


\bibitem{valves_chambers} ŠULC, B. a J. A. JAN. Non Linear Modelling and
Control of Hydraulic Actuators. \textit{Acta Polytechnica}. 2002,
\textbf{42}(3). ISSN 1805-2363. Dostupné z: doi:10.14311/354



\bibitem{simscape} \textit{Simscape Model and simulate multidomain physical
systems} [online]. [cit. 2021-5-21]. Dostupné z:
https://www.mathworks.com/products/simscape.html


\bibitem{ident} System Identification Toolbox. \textit{System
Identification Toolbox} [online]. [cit. 2021-5-21]. Dostupné z:
https://www.mathworks.com/help/ident/


\bibitem{ml} \textit{Statistics and Machine Learning Toolbox} [online].
[cit. 2021-5-21]. Dostupné z:
https://www.mathworks.com/products/statistics.html




\end{thebibliography}

